Higher-Order unification for free!

### 2024-07-01 paper/main.tex
heigenvariables -> eigenvariables

\noindent
The second snippet illustrates the deduplication of \linketa. The syntax
<<\elpiIn{N ~$\triangleright$~ G ?- P}>> denotes a $\lambda$Prolog sequent, that is a 
goal \elpiIn{P} under a set \elpiIn{G} of hypothetical rules (introduced
by \elpiIn{=>}) and where the program context binds (via the \elpiIn{pi}
operator) heigenvariables in \elpiIn{N}. Sequents are presented to
CHR with their higher order unification variables replaced by
``frozen constants'', that is $A_{xyz}$ becomes <<\elpiIn{uvar ~$f_A$~ [x,y,z]}>>
for a fresh constant $f_A$. Frozen constants are ``defrost'' when
they are part of a new goal (see \cite[section 4.3]{TASSI_2019}).

>>>>

\noindent
The second snippet illustrates the deduplication of \linketa. The syntax
<<\elpiIn{N ~$\triangleright$~ G ?- P}>> denotes a $\lambda$Prolog sequent, that is a 
goal \elpiIn{P} under a set \elpiIn{G} of hypothetical rules (introduced
by \elpiIn{=>}) and where the program context binds (via the \elpiIn{pi}
operator) eigenvariables in \elpiIn{N}. Sequents are presented to
CHR with their higher order unification variables replaced by
``frozen constants'', that is $A_{xyz}$ becomes <<\elpiIn{uvar ~$f_A$~ [x,y,z]}>>
for a fresh constant $f_A$. Frozen constants are ``defrost'' when
they are part of a new goal (see \cite[section 4.3]{TASSI_2019}).
